\chapter*{Acknowledgments}

At the end of all this work I want to acknowledge all the people that helped me to arrive so far.

I would like to express my gratitude to my advisor Prof.~\textit{Martino Gagliardi}, for the useful discussions, comments and corrections in the development of this work. Furthermore a special thanks to the examiner of this work Prof.~\textit{Ferruccio Balestra}, the door of his office was always open to students whenever was needed in these five years. 

My special thanks goes to my CERN supervisor \textit{Frank Tecker}, for his guidance and his patience in introducing me in the accelerator world. His constant support was invaluable going though this work.

Thanks to all the people met this year at CERN. To Theo, for the precious advice that goes beyond the mere physics. To Davide for his patience and the help inside and outside of the CTF3. To Irina, for the coffe and the time spent together,  and to Piotr, Jack, Tobias, Lukas, Wilfrid and all the CTF3 people for the help and the advices in this my rookie year playing with accelerators. Your help was great and I got passioned to accelerator physics also because of~you.

Un grazie va alla mia famiglia.  A mia mamma perché c'é sempre stata e a mio pap\`a perché alla fine, se come fisico sperimentale me la cavo, forse é proprio perché da piccolo qualcuno mi ha insegnato a sporcarmi le mani portandomi con sé. A mia zia Delia, non ho parole per descrivere l'aiuto che mi ha dato in questi anni e quanto mi manchi passare anche solo a fare quattro chiacchere per un caff\`e nelle pause studio all'Opera.

To all my friends, I cannot mention you one by one, but: \textit{grazie a Davide e Andrea}, per le notti insonni passate a ciapinare (e se capitava anche a fare un po' di fisica); \textit{grazie a Martina}, per il lavoro e il tempo passato assieme; \textit{grazie agli amici fisici}, per questi anni condivisi in facolt\`a a stingere i denti; \textit{thanks to} the friends meet at CERN, in particular Al, Ola and Philip. You made this year unforgettable.

A thought to my coaches, Enrico, Marco, and all the inspiring people I met so far in my life. You showed me how to deal with problems and taught to never give~up.

\textit{To F. and F.}, both of you are not in my life anymore, but I'm sure you would be happy to see me at this point. If I arrived so far, it is also because of your help. Thanks.

Un ultimo e davvero sentito ringraziamento va al prof. Dario Mottinelli, perché in 5 anni di liceo é riuscito a trasmettere la curiosit\`a e il piacere della scoperta, e solo ora mi rendo conto che per uno scienziato é la qualit\`a pi\`u importante. Tutte le volte che, di fronte a un esperimento fattibile in casa, non ha detto il risultato, ma mi ha risposto "prova !", non ho mai capito quanto bene mi stesse facendo. Ora lo so, e gliene sar\`o sempre grato. A Lei va il mio grazie pi\`u sentito.
\blockquote{
\emph{The mediocre teacher tells. The good teacher explains. The superior teacher demonstrates. The great teacher inspires.}
\begin{flushright}
- William Arthur Ward
\end{flushright}
}%end of blockquote
